How to \underline{not} write Virtual Machines for \mbox{Dynamic Languages}

### 2007-07-28 talk/dyla2007/talk.tex
Insert "general-purpose" before the first "OO VM".
Write down a link to PyPy for interested people.
typos

\begin{frame}
  \frametitle{Common Approaches to VM construction}
  \begin{block}{
    Using C directly (or C disguised as another language)}
    \begin{itemize}
    \item
      CPython
    \item
      Ruby
    \item
      Spidermonkey (Mozilla's JavaScript VM)
    \item
      but also: Squeak, Scheme48
    \end{itemize}
  \end{block}
  \begin{block}{
    Building on top of an existing OO VM}
    \begin{itemize}
    \item
      Jython, IronPython
    \item
      JRuby, IronRuby
    \end{itemize}
  \end{block}
\end{frame}

@@

\begin{frame}
  \frametitle{Implementation Proliferation}
  \begin{itemize}
  \item
    restrictions of the original implementation lead to re-implementations,
    forks
  \item
    all implementations need to be syncronized with language evolution
  \item
    lots of duplicate effort
  \end{itemize}
  \pause
  \begin{block}{
    Python Case}
    \begin{itemize}
    \item
      several serious implementations: CPython, Stackless, Psyco, Jython,
      IronPython, PyPy
    \item
      the implementations have various grades of compliance
    \end{itemize}
  \end{block}
\end{frame}

@@

\begin{frame}
  \frametitle{Open Issues / Drawbacks / Further Work}
  \begin{itemize}
  \item
    writing the translation toolchain in the first place takes lots of effort
    (but it can be reused)
  \item
    writing a good GC is still necessary. but: maybe we can reuse existing good
    GCs (e.g.\ from the Jikes RVM)?
  \item
    conceptually simple approach but many abstraction layers
  \item
    dynamic compiler generation seems to work, but needs more efforts.
    also: can we layer it on top of the JIT of a general purpose OO VM?
  \end{itemize}
\end{frame}

@@

\begin{frame}
  \frametitle{}
  \begin{itemize}
  \item
  \end{itemize}
\end{frame}

>>>>

\begin{frame}
  \frametitle{Common Approaches to VM construction}
  \begin{block}{
    Using C directly (or C disguised as another language)}
    \begin{itemize}
    \item
      CPython
    \item
      Ruby
    \item
      Spidermonkey (Mozilla's JavaScript VM)
    \item
      but also: Squeak, Scheme48
    \end{itemize}
  \end{block}
  \begin{block}{
    Building on top of a general-purpose OO VM}
    \begin{itemize}
    \item
      Jython, IronPython
    \item
      JRuby, IronRuby
    \end{itemize}
  \end{block}
\end{frame}

@@

\begin{frame}
  \frametitle{Implementation Proliferation}
  \begin{itemize}
  \item
    restrictions of the original implementation lead to re-implementations,
    forks
  \item
    all implementations need to be synchronized with language evolution
  \item
    lots of duplicate effort
  \end{itemize}
  \pause
  \begin{block}{
    Python Case}
    \begin{itemize}
    \item
      several serious implementations: CPython, Stackless, Psyco, Jython,
      IronPython, PyPy
    \item
      the implementations have various grades of compliance
    \end{itemize}
  \end{block}
\end{frame}

@@

\begin{frame}
  \frametitle{Open Issues / Drawbacks / Further Work}
  \begin{itemize}
  \item
    writing the translation toolchain in the first place takes lots of effort
    (but it can be reused)
  \item
    writing a good GC is still necessary. But: maybe we can reuse existing good
    GCs (e.g.\ from the Jikes RVM)?
  \item
    conceptually simple approach but many abstraction layers
  \item
    dynamic compiler generation seems to work, but needs more efforts.
    Also: can we layer it on top of the JIT of a general purpose OO VM?
  \end{itemize}
\end{frame}

@@

\begin{frame}
  \frametitle{Links}
  \begin{block}{
    PyPy}
    \bigskip
    \hskip 1cm \url{http://codespeak.net/pypy/}
    \bigskip
  \end{block}
\end{frame}
